\textbf{Computational Fuzzy Extractors}

### 2013-02-15 trunk/CompFuzzExtUnp.tex
starting results on why unpred secure sketches are hard

On the positive side, we show that a different relaxation of the security requirement can in fact lead to a \emph{lossless} construction of secure sketches, in which the knowledge of $s$ does not reduce entropy of $w$ (see Theorem~%s~%\ref{thm:lossless secure sketch} and
~\ref{thm:lossless secure conductor log})).  This relaxation requires that $w$ have high \emph{unpredictability} entropy conditioned on $s$ (unpredictability  entropy is a computational notion originally defined in \cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}).  We demonstrate how to build such lossless sketches based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.

@@

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$. $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.

@@

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.  can we change this $d$ to $\mathsf{dis}$?}

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. An average-case extractor is simply a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^m$ a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), U_d, Y), U_m\times
U_d \times Y) \le \epsilon$.
\end{definition}

%In \secref{sec:defCompFuzzyExtractors} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

@@

\begin{definition}
Let $(X, Z)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Z$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Z)\geq k$ if there exists a collection of
distributions $Y_z$ for each $z\in Z$, giving rise to a joint distribution
$(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((X, Z),(Y,Z))\leq \epsilon$.
\end{definition}

Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.

Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a noisy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from noisy computational conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
Suppose we redefine secure sketches using HILL entropy: that is, an \emph{$(\epsilon,s_{sec})$-HILL-entropy secure sketch} is the same object as in Definition~\ref{def:secure sketch}, but the security requirement is replaced with  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$. 
Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows. Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.  Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y$ with high probability.  In particular, $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.  This means we can construct a set $C$ out of the points in the support of $Y$.  Then $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  
%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.

@@

\ignore{
Finally, we will 
dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).  \lnote{why do we need this definition?}

\begin{definition}
A pair of functions $(\sketch, \rec) $ is a $(s_{rec}, t)$-\emph{recover functionality for a metric space $\mathcal{M}, d$} if $\sketch : \mathcal{M}\rightarrow \{0,1 \}^*$ is a randomized function and $\rec: \mathcal{M}\times \{0, 1\}^*\rightarrow \mathcal{M}$ is a function computable by a circuit of size at most $s_{rec}$, such that $\rec (w', \sketch (w)) = w$ if $\dis(w, w')\leq t$ for all $w, w' \in \mathcal{M}$.
\end{definition}
}

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$. \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

>>>>

On the positive side, we show that a different relaxation of the security requirement can in fact lead to a \emph{lossless} construction of secure sketches, in which the knowledge of $s$ does not reduce entropy of $w$ (see Theorem~%s~%\ref{thm:lossless secure sketch} and
~\ref{thm:lossless secure sketch log})).  This relaxation requires that $w$ have high \emph{unpredictability} entropy conditioned on $s$ (unpredictability  entropy is a computational notion originally defined in \cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}).  We demonstrate how to build such lossless sketches based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.

@@

\section{Preliminaries}
\label{sec:preliminaries}
We begin by recalling a few basic entropy definitions.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized $\{0,1\}$ distinguishers of size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.

@@

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1, 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.  can we change this $d$ to $\mathsf{dis}$?}

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that if $\dis(w,w')\leq t$ and $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}
A fuzzy extractor can be produced from a \emph{average-case randomness extractor} %(all randomness extractors are average-case extractors with a small loss, see~\cite[Chapter 6]{vadhan2012}) 
and a \emph{secure sketch}.  
An average-case extractor is simply a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
An extractor $\ext$ is a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), Y), U_m\times
U_d \times Y) \le \epsilon$.
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t, \epsilon)$-\emph{approximately correct secure sketch} is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',SS(w))=w]\geq 1-\epsilon$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|SS(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time.  If $\epsilon=0$ we omit $\epsilon$ and say that $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch}.
\end{definition}
For an approximately correct secure sketch we assume that errors are drawn independently of $\sketch(w)$.  If the error pattern between $w$ and $w'$ depends on $\sketch(w)$ there is no guarantee about the probability of correctness.
%In \secref{sec:defCompFuzzyExtractors} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
A fuzzy extractor is usually formed by combining a randomness extractor with a secure sketch.
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor~(for $(r, x)$ drawn from the uniform distribution):
\begin{itemize}
\item $\gen(w; r, x):$ set $P=(\sketch(w; r), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

@@

\begin{definition}
Let $(X, Y)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Y$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Y)\geq k$ if there exists a collection of
distributions $Z_y$ for each $y\in Y$, giving rise to a joint distribution
$(Z, Y)$, such that $\tilde{H}_\infty(Z|Y)\geq k$ and for all (randomized, binary output) circuits $D$ of size $s_{sec}$, $\delta^D((X, Y),(Z,Y))\leq \epsilon$.
\end{definition}

Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches can't perform much better than the information-theoretic ones.

Instead, in \secref{sec:unp secure sketch}, we define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  In particular, in \secref{sec:comp fuzzy extractors}, we show a natural construction of computational fuzzy extractors from secure sketches defined using unpredictability.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
It seems natural to replace a sketch that retains information theoretic entropy with a sketch that retains HILL entropy.  Then the paradigm of secure sketch and average case randomness extractor could be used. However, we show that using this definition it is impossible to beat information theoretic bounds on secure sketches.  We omit formal definitions for the moment and recall the two informal properties we seek:
\begin{itemize}
\item \emph{Correctness}: if $\dis(w, w')\leq t$ then $\rec(w', \sketch(w)) = w$.
\item \emph{Security}: For all $W$ where $H_\infty(W)\geq m$, $H^\hill_{\epsilon, s}(W|\sketch(W))  = \tilde{m}$.
\end{itemize}
%We will concentrate on the case where $gap = m-\tilde{m}=0$ however, any setting where  $gap$ is better than the best information theoretic sketch is still a meaningful result. % As before, we desired $\rec$ to be efficiently computable.  We start with this stronger definition to show the difficulty of constructing such an object.

Unfortunately, we will show if $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$ this implies an error correcting code with approximately $2^{\tilde{m}}$ points.  We provide intuition for the argument below and then present the formal argument.  Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  This means in order for $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$, there must be a distribution $Y$ where $\Hoo(Y)\geq \tilde{m}$ such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.  This means the points in $Y$ form an error correcting code and $\rec$ is an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  This means lower bounds on the entropy loss of an information theoretic sketch must apply.  There are several technical conditions required to make this intuition formal, we present them below.
%any function that is able to recover correctly on a large space is an decoder for an error correcting code formed by that space.  If there is a distribution $Y$ with many points such that $\rec(y', \sketch(w)) =y\in Y$ when $\dis(y, y')\leq t$.  Then $\rec$ is a decoder for the error correcting code formed by $Y$.
% and make no assumption about the behavior of $\rec $ outside of this ball.  The intuition is quite simply, on a point $w\leftarrow W$, the \rec oracle will always return $w$ within the $B_t(w)$.  If $W|\sketch(W)$ is indistinguishable from $Y|\sketch(W)$ then the $\rec$ oracle must also correct for points in $Y$.  However, this implies a code~(the points in $Y$) with $\rec$ as an efficient decoding algorithm. 
%\subsubsection{The Uniform Distribution}
%and extend to an arbitrary high-entropy distribution.  
%We begin by showing that any given no distribution $W$ can be indistinguishable from the uniform distribution given a sketch.
%We need two technical requirements on our metric space: 1) there is an efficient algorithm to sample neighbors 2) each point is regular~(has the same number of neighbors).  These requirements hold for several natural metric spaces including Hamming and symmetric difference metrics.
%The only other requirement we make is for the distribution and its neighborhood to be efficiently samplable.
%\begin{definition}
%A distribution $W$ is $s-$\emph{efficiently-samplable} if there exists a randomized circuit of size at most $s$ that outputs samples according to $W$.
%Furthermore, we say $W$ is \emph{efficiently-samplable} if there exists a randomized circuit of polynomial size that outputs samples according to $W$.
%\end{definition}
%We will be working with a metric space $\mathcal{M}, d$.  We will need to efficiently sample nearby points in the metric space.
We assume that sampling a random neighbor of a point is efficient:
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit, $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
Furthermore, there is a procedure that outputs a random point of distance at most $t$.  For convenience we denote this procedure by $\sample(X)$.
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, this is not very interesting in the context of fuzzy extractors~(as \gen can always output the empty string for $P$).

@@

Finally, we will dealing with an arbitrary secure sketch that only needs to satisfy the correctness property of a secure sketch~(see \defref{def:secure sketch}).

\begin{definition}
A pair of functions $(\sketch, \rec) $ is a $(s_{rec}, t)$-\emph{recover functionality for a metric space $\mathcal{M}, d$} if $\sketch : \mathcal{M}\rightarrow \{0,1 \}^*$ is a randomized function and $\rec: \mathcal{M}\times \{0, 1\}^*\rightarrow \mathcal{M}$ is a function computable by a circuit of size at most $s_{rec}$, such that $\rec (w', \sketch (w)) = w$ if $\dis(w, w')\leq t$ for all $w, w' \in \mathcal{M}$.
\end{definition}

@@

We show that any recovery functionality that retains high HILL entropy implies a information theoretic secure sketch.  We begin by reviewing definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t)) \neq c]<\epsilon$.
\end{definition}
This is a slightly nonstandard formulation, we only require the code to correct exactly $t$ errors\footnote{In the standard formulation, the code must correct up to $t$ errors.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.  Shannon codes work for all codewords, we can also consider a formulation that works for an ``average'' codeword.
\begin{definition}
Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that 
$\Pr_{w\leftarrow W}[\rec(\sample(w, t)) \neq w]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a (maximal error)~Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements}~(we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $W'$ where $|W'|\ge2^{k-1}$ and $W'$~(drawing a codeword uniformly) is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}
